\ifthenelse{\boolean{en}}{\section{Personal References}}{\section{Referências Pessoais}}
	\begin{tabularx}{\linewidth}{>{\raggedleft\scshape}p{2.1cm}X}
    \ifthenelse{\boolean{en}}{
		& Aline Carneiro Viana. Research Scientist, INRIA, France. \linebreak {\carta} aline.viana@inria.fr \\
		& \\
		& Antonio A. F. Loureiro. Titular Professor of the Computer Science Department at Federal University of Minas Gerais, Brazil. {\carta}~loureiro@dcc.ufmg.br \\
		& \\
		& Pedro Olmo S. V. de Melo. Professor of the Computer Science Department at Federal University of Minas Gerais, Brazil. {\carta}~olmo@dcc.ufmg.br \\
		& \\
		& Heitor S. Ramos. Professor of the Institute of Computing at Federal University of Alagoas, Brazil. {\carta}~ramosh@acm.org \\
		& \\
		& Leandro A. Villas. Professor of the Computing Systems Department at State University of Campinas, Brazil. {\carta}~leandro@ic.unicamp.br \\
		& \\
		& Carlos Sarraute, Director of R\&D at GranData, Argentina. {\carta}~charles@grandata.com \\
		& \\
		& Raquel A. F. Mini. Coordinator of Computer Science Department in Pontifical Catholic University of Minas Gerais, Brazil. {\carta}~raquelmini@pucminas.br\\
		& \\
		& Tales Lacerda. Director of Task Software, Minas Gerais, Belo Horizonte, Brazil. {\carta}~tales@task.com.br \\
    } {
    & Aline Carneiro Viana. Cientista Pesquisadora, INRIA, França. {\carta}~aline.viana@inria.fr \\
		& \\
    & Antonio A. F. Loureiro. Professor Titular do Departamento de \cc da \ufmg. {\carta}~loureiro@dcc.ufmg.br \\
		& \\
		& Pedro Olmo Stancioli Vaz de Melo. Professor do Departamento de \cc da \ufmg. {\carta}~olmo@dcc.ufmg.br \\
		& \\
		& Heitor S. Ramos. Professor do Instituto de Computação na Universidade Federal de Alagoas. {\carta}~ramosh@acm.org \\
		& \\
		& Leandro Aparecido Villas. Professor do Departamento de Sistemas de Computação na Unicamp. {\carta}~leandro@ic.unicamp.br \\
		& \\
		& Carlos Sarraute, Diretor de R\&D na GranData, Argentina. {\carta}~charles@grandata.com \\
		& \\
		& Raquel A. F. Mini. Coordenadora do Curso de Ciência da Computação na \puc. {\carta}~raquelmini@pucminas.br\\
		& \\
		& Tales Lacerda. Diretor da Task Software, Belo Horizonte, Minas Gerais. {\carta}~tales@task.com.br \\
    }
	\end{tabularx}
