\section{Some Open Source Projects} \label{sec:open_source}

\cvitem{}{\textbf{Benchmark XGBoost Java} \linktopage{https://github.com/edumucelli/benchmark-xgboost-java}}
\cvitem{}{Comprehensive benchmark of XGBoost libraries for Java.}

\cvitem{}{\textbf{Twitter applet} \linktopage{https://code.launchpad.net/\~eduardo-mucelli/cairo-dock-plug-ins-extras/Twitter}}
\cvitem{}{Twitter applet for Cairo-Dock which handles most of Twitter's API features, including streaming.}

%\cvitem{}{\textbf{WebSearch applet} -- Code %\linktopage{https://code.launchpad.net/\~eduardo-mucelli/cairo-dock-plug-ins-extras/WebSearch}}
%\cvitem{}{Metasearch applet for Cairo-Dock capable of retrieving text and image results from several sources, e.g., Google, Bing, Yahoo!, Youtube, and Twitter.}

\cvitem{}{\textbf{Repeat One Song} \linktopage{https://github.com/edumucelli/repeat-one-song}}
% \cvitem{}{\textbf{Python}}
\cvitem{}{The Repeat One Song feature for Rhythmbox.}

% \begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2.1cm}X}
% 	\gray \ptitle & \textbf {RubyBikes} \\
%     \gray \planguage & \textbf {Ruby} (Code \href{https://github.com/eduardom}{code}) \\
% 		%\gray URL & \textbf{\url{https://launchpad.net/rhythmidgin}} \\
% 			& \ifthenelse {\boolean{en}}
%                       {Ruby Gem that scrapes and aggregates real-time information of bike-sharing systems around the world.}
%                       {Gem Ruby que coleta e agrega informação em tempo real de sistemas de bicicletas públicas do mundo todo.} \\
%             &
% \end{tabularx}

\ifthenelse {\boolean{everything}} {
	\cvitem{}{\textbf{Translator} \linktopage{https://code.launchpad.net/\~eduardo-mucelli/cairo-dock-plug-ins-extras/Translator}}
	\cvitem{}{Full-featured Google Translator-based applet for Cairo-Dock.}
	
    \cvitem{}{\textbf{Quote} \linktopage{https://code.launchpad.net/\~eduardo-mucelli/cairo-dock-plug-ins-extras/Quote}}
    \cvitem{}{"Quote of the day" applet for Cairo-Dock. It crawls Internet sources, e.g., Bash.org, Xkcdb.com, Qdb.us.}
	
	\cvitem{}{\textbf{Rhythmidgin} \linktopage{https://launchpad.net/rhythmidgin}}
	\cvitem{}{Show to Pidgin buddies what is the song you're listening to with Rhythmbox.}

	\cvitem{}{\textbf{Liferea} \linktopage{https://code.launchpad.net/\~eduardo-mucelli/cairo-dock-plug-ins-extras/Liferea}}
	% \cvitem{}{\textbf{Python}}
	\cvitem{}{Applet that provides to Cairo-Dock an interface with Liferea feed news aggregator.}
}{}