\section{Professional Experiences}
\newcommand*{\cvsimple}[4][.25em]{
\begin{tabular*}{\maincolumnwidth}{l@{\extracolsep{\fill}}r}%
	% {\bfseries #4} & {\bfseries #5}\\%
	{\itshape #3} & {\itshape #2}\\%
\end{tabular*}%
\ifx&#4&%
\else{\\%
	\begin{minipage}{\maincolumnwidth}%
		\small#4%
\end{minipage}}\fi%
\par\addvspace{#1}}

\cventry{\january 2023 -- Present}{\sse}{Synthesia}{Remote}{}{
	Working on improving the robustness of the video generation.
}
\cventry{\december 2021 -- \november 2022}{\seii}{Canonical}{Remote}{}{
	Improving the data pipeline Python codebase to serve technical and non-technical internal teams.
	Working on the service behind \href{https://ubuntu.com/security/livepatch}{Livepatch} in Golang.
}
% Add second entry to the same company https://tex.stackexchange.com/a/294612
\cvsimple{\june 2020 -- \november 2021}{\se}{
	Working on the services behind \href{https://ubuntu.com/advantage}{Ubuntu Advantage} in Golang and Python.
	Introduced a BDD suite to our main Golang services.
	Revamping team's data pipelines: large refactoring of the Python codebase, type checking, linting, moving from Openstack to Kubernetes (Argo), Grafana, Prometheus, Pushgateway, alerting.
}
\cventry{\july 2016 -- \may 2020}{\se}{BlaBlaCar}{\protect\france}{}{
	Developed features, optimized performance, deployed and monitored a dozen of Java services at the Trip Search team. \href{https://medium.com/blablacar-tech/fast-machine-learning-predictions-6856b3623e5}{Wrote and integrated the first library} to handle Machine Learning predictions at scale for \href{https://github.com/edumucelli/benchmark-xgboost-java}{which I have extensively measured performance}. Significantly worked on the \href{https://blog.blablacar.com/newsroom/news-list/new-search-logo-visual-identity}{new search, routing and matching algorithm}. Main technologies were Java, Elasticsearch, PostgreSQL, PostGIS, XGBoost, OSRM, MySQL and Redis, R and Python.
}
\cventry{\june 2015 -- \june 2016}{Postdoctoral Researcher}{Orange}{\protect\france}{}{
	Developed machine-learning assisted techniques to predict users' QoE based on network's KPIs.
}
\cventry{\july 2011 --- \september 2011}{\se}{Dito Internet}{\protect\brazil}{}{
	Developed in Ruby on Rails, as part of a team, Telecom Italia Mobile's project called TIM Beta, \textit{\href{www.timbeta.com.br}{timbeta.com.br}}.
}
\cventry{\november 2010 --- \may 2011}{Researcher Intern}{Telecom Italia Future Centre}{\protect\italy}{}{
	Developed, in Python, a project called Future of Enterprises aiming to improve the real-time interaction among employees.
}
\cventry{\february 2008 --- \february 2009}{\se}{Task Internet}{\protect\brazil}{}{
	Lead developer of a social network in Ruby on Rails.
}