\ifthenelse {\boolean{everything}} {
	\section{
		\texorpdfstring{
			Publications \linktopage{https://scholar.google.com/citations?user=pD4KMUsAAAAJ}
		}{link}
	}
}{
	\section{
		\texorpdfstring{
			Recent publications \linktopage{https://scholar.google.com/citations?user=pD4KMUsAAAAJ}
		}{link}
	}
}
\begin{itemize}
\item \cvitem{}{Machine Learning for Predicting QoE of Video Streaming in Mobile Networks, IEEE ICC Communication QoS, reliability and modeling symposium, May 2017.  \linktopage{https://ieeexplore.ieee.org/document/7996604}}
\item \cvitem{}{Mobile Data Traffic Modeling: Revealing Temporal Facets, Elsevier Computer Networks, November 2016. \linktopage{https://hal.inria.fr/hal-01073129v5/document}}
\item \cvitem{}{On the regularity of human mobility, Elsevier Pervasive and Mobile Computing, May 2016. \linktopage{https://hal.inria.fr/hal-01367825/document}}
\ifthenelse {\boolean{long}} {
	\item \cvitem{}{Oliveira, Eduardo Mucelli Rezende and Carneiro Viana, Aline and Naveen, K. P. and Sarraute, Carlos., \emph{"Analysis and Modeling of Mobile Data Traffic in Mexico City"}, NetMob, April 2015, Mit Media Lab, Cambridge, MA, United States.}
	\item \cvitem{}{Oliveira, Eduardo Mucelli Rezende and Carneiro Viana, Aline and Naveen, K. P. and Sarraute, Carlos., \emph{"Measurement-driven mobile data traffic modeling in a large metropolitan area"}, IEEE Percom, March 2015, Saint Louis, United States.}
	\item \cvitem{}{Oliveira, Eduardo Mucelli Rezende and Viana, Aline Carneiro., \emph{"From Routine to Network Deployment for Data Offloading in Metropolitan Areas"}, IEEE SECON, June 2014, Singapore.}
	\item \cvitem{}{Oliveira, Eduardo Mucelli Rezende and Viana, Aline Carneiro., \emph{"Routine-based Network Deployment"}, IEEE INFOCOM, Student workshop, April 2014, Toronto, Canada.}
	\item \cvitem{}{Oliveira, Eduardo Mucelli Rezende and Viana, Aline Carneiro., \emph{"From Routine To Better Network Services"}, IEEE/IFIP WMNC, May 2014, Algarve, Portugal.}
	\item \cvitem{}{Oliveira, Eduardo Mucelli Rezende and Viana, Aline Carneiro., \emph{"Routine-based network deployment for data offloading in metropolitan areas"}, IEEE WCNC 2014, Istanbul, Turkey.}
	\ifthenelse {\boolean{everything}} {
		\item \cvitem{}{Oliveira, Eduardo Mucelli Rezende and Viana, Aline Carneiro., \emph{"From your routine to hotspot deployment for data offloading"}, ACM CoNEXT Student 2012, Nice, France.}
		\item \cvitem{}{Oliveira, Eduardo M. R., Ramos, Heitor S., Loureiro, Antonio A. F., \emph{"Centrality-based routing for Wireless Sensor Networks"}, IEEE Wireless Days (WD), 2010 IFIP, Venice, Italy.}
		\item \cvitem{}{Oliveira, Eduardo Mucelli Rezende, O. S. V. M., Pedro, Mini, R. A. F. Comunicação, Codificação e Fusão de Dados para uma Aplicação de Detecção de Incêndios utilizando Redes de Sensores sem Fio \emph{"Data Codification, Fusion and Communication in Wireless Sensors Networks"}, 1º Workshop on Pervasive and Ubiquitous Computing, 2007, Gramado, RS, Brazil.}
	}{}
}{}
\end{itemize}