%-----       letter       ---------------------------------------------------------
% recipient data
% \recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
\recipient{Dailymotion team}{}
\date{\today}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
% \enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I am a Ph.D. in Computer Science at École Polytechnique, France. My Thesis tackled characterization, planning, and deployment problems of urban wireless networks using large-scale datasets of human mobility and data traffic. Besides, I am Linux and Open Source enthusiast for 15 years now. I have \hyperref[sec:open_source]{several projects}, created on my spare time.

Furthermore, I have made the full-stack development of \hyperref[sec:web_app]{three web applications}. E.g., from the \textit{"\href{http://easy.bike}{Easy.Bike}'s"} real-time back-end crawlers, R-based statistics on \textit{"\href{http://www.proconfie.com}{Proconfie}"}, to the front-end on \textit{"\href{http://www.cepaberto.com}{CEP Aberto}"}, and the Apache and MySQL fine-tuning for the three of them within the same VPS.

% Briefly, the first, \textit{"\href{http://easy.bike}{Easy.Bike}"} is a free application that helps bike-sharing cyclers to find the best bicycle stations and route from their places to their destinations. The second, \textit{"\href{http://www.proconfie.com}{Proconfie}"}, is a free application that helps people to choose companies based on historical problems presented with other customers. It received Honorary Mention award from the Brazilian Ministry of Justice. Finally, \textit{"\href{http://www.cepaberto.com}{CEP Aberto}" (Open Postal Code)} is a free and collaborative application that aims to open publicly the Postal Code geolocalized data in Brazil, which even after several popular requests, can be only accessed by those who pay an absurd amount of money for the Brazilian Post-mail service. It provides an API for developers willing to use the Postal Code data and, for the end-users, the possibility to edit, add, fix, follow, specific postal-coded-locations in order to improve the quality of the data.

% I have worked and experienced multicultural environments. I was born in Brazil, coursed part of my Master's Degree in Italy and, since 2011, I live in France. Besides Portuguese, I speak English, French, and Italian.

I was exactly looking for job in which I could apply my knowledge, enthusiam, and workforce. I would like to do that full-time, not only during my spare time, an that is why I am applying for the Software Architect API position at Dailymotion. 

I've already worked and created APIs, notably worked with Twitter's API when developing an open-source applet for Cairo-Dock, which goes from the OAuth authentication to the user's streaming capability. Besides, I work daily my own projects' APIs, open-source, high-level programming as Python, Ruby and Javascript.

If that is from you interest, I'd be highly interested in meeting you to discuss how my experiences can aggregate to Dailymotion.

\makeletterclosing